Cover letter for the IJRR submission \\ ``An efficient acyclic contact planner for multiped robots''

### 2016-01-17 body/abstract.tex
trajectory removed

We address the issue of automatically planning discrete sequences of contacts
that characterize a multiped motion in an arbitrary cluttered environment.
To overcome the inherent combinatorial difficulty of this problem, we separate it
in two sub-problems: first, planning a guide path for the root of the robot and
then, generating relevant contacts along this path.
We propose theoretical contributions for each sub-problem, and implement them
as a complete contact planner. 
First, we propose a geometrical characterization of a guide trajectory, the ``reachability condition", which guarantees that a
guide can be mapped into the contact manifold of the robot. With this condition, asserting the``true feasibility" 
of a guide path boils down to performing collision tests, thus avoiding the expensive explicit computation of balanced contact configurations, as opposed to previous approaches.
Then, we propose a sequential algorithm to extend a truly feasible path into a sequence of contacts. For each limb, an off-line sampling approach,
independent from the environment, is run once and for all, and used at run time to provide efficiently candidate configurations for contact.
The best candidate is chosen according to user-defined heuristics. We propose two such heuristics, used in all our experiments, and 
designed for generic robotic applications: a manipulability-based heuristic, EFORT, and a robustness criterion regarding the balance of the robot.
These contributions are implemented within the open-source software Hpp. Our framework allows us to generate complex multi-contact sequences for a large
variety of robots, including HRP-2, HyQ, and a dexterous hand, with interactive performances.

>>>>

We address the issue of automatically planning discrete sequences of contacts
that characterize a multiped motion in an arbitrary cluttered environment.
To overcome the inherent combinatorial difficulty of this problem, we separate it
in two sub-problems: first, planning a guide path for the root of the robot and
then, generating relevant contacts along this path.
We propose theoretical contributions for each sub-problem, and implement them
as a complete contact planner. 
First, we propose a geometrical characterization of a guide path, the ``reachability condition", which guarantees that a
guide can be mapped into the contact manifold of the robot. With this condition, asserting the``true feasibility" 
of a guide path boils down to performing collision tests, thus avoiding the expensive explicit computation of balanced contact configurations, as opposed to previous approaches.
Then, we propose a sequential algorithm to extend a truly feasible path into a sequence of contacts. For each limb, an off-line sampling approach,
independent from the environment, is run once and for all, and used at run time to provide efficiently candidate configurations for contact.
The best candidate is chosen according to user-defined heuristics. We propose two such heuristics, used in all our experiments, and 
designed for generic robotic applications: a manipulability-based heuristic, EFORT, and a robustness criterion regarding the balance of the robot.
These contributions are implemented within the open-source software Hpp. Our framework allows us to generate complex multi-contact sequences for a large
variety of robots, including HRP-2, HyQ, and a dexterous hand, with interactive performances.

### 2016-01-17 body/contact.tex
cosmetics, added title, extended conclusion
trajectory removed

We first define $C_{Contact}^{\epsilon} \supset C_{Contact}$ as the set of configurations almost in contact. This means that the minimal distance 
between an effector and a surface of the environment is less than a small value $\epsilon$.
We then apply the following steps:
\begin{enumerate}
\item Generate off-line $N$ valid sample limb configurations $\mathbf{q}^k_i,  0 \leq i < N$;
\item Using the end-effector positions $\mathbf{p}(\mathbf{q}^k_i)$ as indices, store each sample in an octree stata structure;
\item Figure~\ref{fig:contact_gen}--b and c--: At runtime, when contact creation is required, retrieve from the octree the list of samples $S \subset C_{Contact}^{\epsilon}$ close to contact;
\item According to a user-defined heuristic $h$, sort the elements of $S$;
\item Figure~\ref{fig:contact_gen}--d and e--: Select the first configuration of $S$ (or fail if $S$ is empty). Project the configuration onto contact with inverse kinematics;
\item If a valid solution is found, stop. Otherwise remove the element from $S$ and go back step 5.
\end{enumerate}

@@

\subsection{Extension of the guide trajectory}
Using the contact generator, we define an iterative algorithm to generate the contact
sequence along the guide path.
Although we address acyclic contact sequences, the algorithm is deterministic in the order in which 
the contacts are created, allowing it to break the combinatorial.
The complete algorithm can be found in Appendix~\ref{app:contact}.
In the remainder of the section we provide an intuition of it.

>>>>

We first define $C_{Contact}^{\epsilon} \supset C_{Contact}$ as the set of configurations almost in contact. This means that the minimal distance 
between an effector and a surface of the environment is less than a small value $\epsilon$.
We then apply the following steps:
\begin{enumerate}
\item Generate off-line $N$ valid sample limb configurations $\mathbf{q}^k_i,  0 \leq i < N$;
\item Using the end-effector positions $\mathbf{p}(\mathbf{q}^k_i)$ as indices, store each sample in an octree data structure;
\item Figure~\ref{fig:contact_gen}--b and c--: At runtime, when contact creation is required, retrieve from the octree the list of samples $S \subset C_{Contact}^{\epsilon}$ close to contact;
\item According to a user-defined heuristic $h$, sort the elements of $S$;
\item Figure~\ref{fig:contact_gen}--d and e--: Select the first configuration of $S$ (or fail if $S$ is empty). Project the configuration onto contact with inverse kinematics;
\item If a valid solution is found, stop. Otherwise remove the element from $S$ and go back step 5.
\end{enumerate}

@@

\subsection{Extension of the guide path}
Using the contact generator, we define an iterative algorithm to generate the contact
sequence along the guide path.
Although we address acyclic contact sequences, the algorithm is deterministic in the order in which 
the contacts are created, allowing it to break the combinatorial.
The complete algorithm can be found in Appendix~\ref{app:contact}.
In the remainder of the section we provide an intuition of it.

### 2016-01-17 body/intro.tex
trajectory removed

As suggested by \citeauthor{Bouyarmane2009}, we believe that these two tasks can be treated sequentially within a global planner, while preserving the completeness of the search.
We go further and claim that this can be done at a much smaller cost, provided that necessary and sufficient conditions for contact feasibility can be formulated for the robot trajectory.
This paper presents a geometrical representation of these conditions, and a concrete implementation of such a decoupled planner.
This implementation results from a trade-off between a necessary and a sufficient condition for feasibility, allowing us to find solutions extremely fast.
while preserving a high success rate in the demonstrated scenarios.

@@

The issue of planning acyclic contacts was first completely described by \citeauthor{Bretl:2006:MPM:1124573.1124585} in their seminal paper. The issue requires the simultaneous handling of two problems, $\mathcal{P}_1$: Planning a relevant guide trajectory for the root of the robot in $SE(3)$; and $\mathcal{P}_2$: Planning a discrete sequence of acyclic contact configurations along the trajectory (A third nontrivial problem, $\mathcal{P}_3$, not addressed in this work, then consists in interpolating a complete motion between two postures of the contact sequence).  A key issue is to avoid combinatorial explosion when considering at the same time the possible contact configurations and the potential trajectories. This seminal paper proposes a first effective algorithm, able to handle simple situations (such as climbing scenarios), but not applicable to arbitrary environments. Following it, seve\-ral papers have applied this approach in particular situations, typically limiting the combinatorial by imposing a fixed set of possible contacts \citep{Hauser06usingmotion, stilman2010}.

@@

\textbf{On the other hand, the two problems \Pa and \Pb might be decoupled} to reduce the complexity. The feasibility and interest of the decoupling is shown by \citeauthor{DBLP:conf/iser/EscandeKMG08} who manually set up a rough guide trajectory (i.e. an ad-hoc solution to $\mathcal{P}_1$). \Pb  is then addressed as the combinatorial computation of a feasible contact sequence in the neighborhood of the guide. A solution can then be found, efficiently when considering quadruped locomotion \citep{kalakrishnan2011learning}, but at the cost of prohibitive computation times (several hours) for constrained scenarios for humanoid. In the latter case, this approach is suboptimal because the quality of the motion is conditioned by the quality of the guide trajectory,  which is not evaluated \textit{a priori}. \citeauthor{Bouyarmane2009} precisely focus on automatically computing a guide trajectory with guarantees of contact feasibility, by extending key frames of the trajectory into whole-body contact configurations in static equilibrium. Randomly sampled configurations are projected into the contact sub-manifold using a generalized inverse kinematics solver, a computationally expensive process (about 15 minutes are required to compute a guide trajectory in the examples presented). Moreover this explicit projection is yet an insufficient condition and does not provide strong guarantees on the feasibility of the path between two key positions in the trajectory. \citeauthor{7140082} also propose a decoupled approach, with a planning phase based on the reachable workspace of the robot limbs, that characterize the ability to create a contact with 
a discretized environment. This planning phase does not account for collisions, involving that replanning is required in case of failure. This approach is efficient 
in the scenarios demonstrated. In extremely constrained cases such 
as the car egress scenario we address here, we believe that including collision constraints in the planning is a requirement.

@@

It thus appears that, regarding robotics applications, an integrated optimization-based approach \citep{Mordatch:2012:DCB:2185520.2185539}, able to generate a locally-optimal, complete trajectory within minutes, currently outperforms existing planners, decoupled or not. However, recent contributions are able to interpolate dynamically-feasible
trajectories between contact configurations \citep{Hauser2014, herzog2015trajectory, Park116, Carpentier2016}. \citeauthor{Carpentier2016} are able to achieve this with real-time performances on the real robot.
To generate the input contact configurations, there is a need for an efficient contact planner, able to break the combinatorial to generate discrete contact sequences rapidly. 
Such a planner holds the promise of a complete real-time multi-contact locomotion system.

\subsection{Rationale}
This paper presents a pragmatic approach to break the complexity of multi-contact planning. With that objective in mind,
we believe that the separation between the generation of the guide trajectory and the contact sequence is the most promising direction \citep{DBLP:conf/iser/EscandeKMG08}.
However, this direction raises two theoretical questions that remain to be solved, or even to be properly formulated. \\

\noindent \textbf{Regarding $\mathcal{P}_1$}, the guide trajectory must guarantee the existence of a contact sequence to actuate it (This property is related to the controllability of the root actuated by the contact forces). We call this property \textit{true feasibility}. This property has not been studied yet; the only way to validate a waypoint in the trajectory is to explicitly compute the contact locations and forces, which is computationally not reasonable \citep{Bouyarmane2009}, unless the scenario is limited to cyclic, quasi-flat cases \citep{zucker2010optimization}. \\

\noindent \textbf{Regarding $\mathcal{P}_2$}, there are infinite combinations of possible contact sequences for a given root trajectory. The selection of one particular contact sequence with interesting properties (minimum number of contact changes, robustness, efficiency or naturalness) has been studied for cyclic cases \citep{Hauser06usingmotion}, but has not been efficiently applied to cluttered environments (\citeauthor{bouyarmane:lirmm-00777727, DBLP:conf/iser/EscandeKMG08} mostly randomly picked one contact sequence, leading to possibly very tedious transitions).  \\

@@

Compared to previous work \citep{Mordatch:2012:DCB:2185520.2185539} our planner does not produce a complete motion, but a discrete sequence of contacts.
Since the interpolation of a complete trajectory between such configurations can be solved within real-time constraints \citep{Carpentier2016}, we claim that our planner
is the fastest multi-contact planning solution to our knowledge.

\begin{figure*}
  \centering
  \begin{overpic}[width=0.8\linewidth]{figures/workflow}
    %~ \put (6.4,1.8) {\normalsize{Request}} 
    \put (30,10.8) {\large{\color{white}\Pa} }
    %~ \put (31.6,2) {\scriptsize{\color{white}RB-RRT}} 
    \put (66.4,10.8) {\large{\color{white}\Pb} }
    %~ \put (72.5,2) {\tiny{\color{white}Contact}} 
  \end{overpic}
  \vspace{-1em}
  \caption{
    Overview of our 2-stage framework. \Pa: Given a path request between the yellow and blue positions, a guide path is computed in the space of truly feasible guides $C_{reach}$. This is achieved by defining a geometric condition, the reachability condition (abstracted here with the transparent cylinders). \Pb: The trajectory is extended into a discrete sequence of contact configurations using an iterative algorithm.}
  \label{fig:framework}
\end{figure*}

>>>>

As suggested by \citeauthor{Bouyarmane2009}, we believe that these two tasks can be treated sequentially within a global planner, while preserving the completeness of the search.
We go further and claim that this can be done at a much smaller cost, provided that necessary and sufficient conditions for contact feasibility can be formulated for the robot path.
This paper presents a geometrical representation of these conditions, and a concrete implementation of such a decoupled planner.
This implementation results from a trade-off between a necessary and a sufficient condition for feasibility, allowing us to find solutions extremely fast.
while preserving a high success rate in the demonstrated scenarios.

@@

The issue of planning acyclic contacts was first completely described by \citeauthor{Bretl:2006:MPM:1124573.1124585} in their seminal paper. The issue requires the simultaneous handling of two problems, $\mathcal{P}_1$: Planning a relevant guide path for the root of the robot in $SE(3)$; and $\mathcal{P}_2$: Planning a discrete sequence of acyclic contact configurations along the path (A third nontrivial problem, $\mathcal{P}_3$, not addressed in this work, then consists in interpolating a complete motion between two postures of the contact sequence).  A key issue is to avoid combinatorial explosion when considering at the same time the possible contact configurations and the potential paths. This seminal paper proposes a first effective algorithm, able to handle simple situations (such as climbing scenarios), but not applicable to arbitrary environments. Following it, seve\-ral papers have applied this approach in particular situations, typically limiting the combinatorial by imposing a fixed set of possible contacts \citep{Hauser06usingmotion, stilman2010}.

@@

\textbf{On the other hand, the two problems \Pa and \Pb might be decoupled} to reduce the complexity. The feasibility and interest of the decoupling is shown by \citeauthor{DBLP:conf/iser/EscandeKMG08} who manually set up a rough guide path (i.e. an ad-hoc solution to $\mathcal{P}_1$). \Pb  is then addressed as the combinatorial computation of a feasible contact sequence in the neighborhood of the guide. A solution can then be found, efficiently when considering quadruped locomotion \citep{kalakrishnan2011learning}, but at the cost of prohibitive computation times (several hours) for constrained scenarios for humanoid. In the latter case, this approach is suboptimal because the quality of the motion is conditioned by the quality of the guide path,  which is not evaluated \textit{a priori}. \citeauthor{Bouyarmane2009} precisely focus on automatically computing a guide path with guarantees of contact feasibility, by extending key frames of the path into whole-body contact configurations in static equilibrium. Randomly sampled configurations are projected into the contact sub-manifold using a generalized inverse kinematics solver, a computationally expensive process (about 15 minutes are required to compute a guide path in the examples presented). Moreover this explicit projection is yet an insufficient condition and does not provide strong guarantees on the feasibility of the path between two key positions in the path. \citeauthor{7140082} also propose a decoupled approach, with a planning phase based on the reachable workspace of the robot limbs, that characterize the ability to create a contact with 
a discretized environment. This planning phase does not account for collisions, involving that replanning is required in case of failure. This approach is efficient 
in the scenarios demonstrated. In extremely constrained cases such 
as the car egress scenario we address here, we believe that including collision constraints in the planning is a requirement.

@@

Interpolation between contact poses ($\mathcal{P}_3$) remains an unsolved problem,
though recent contributions have been able to bring partial solutions to it \citep{Hauser2014, herzog2015trajectory, Park116, Carpentier2016}. \citeauthor{Carpentier2016} are able to achieve this with real-time performances on the real robot.
To generate the input contact configurations, there is a need for an efficient contact planner, able to break the combinatorial to generate discrete contact sequences rapidly. Such a planner holds the promise of a complete real-time multi-contact locomotion system.

\subsection{Rationale}
This paper presents a pragmatic approach to break the complexity of multi-contact planning. With that objective in mind,
we believe that the separation between the generation of the guide path and the contact sequence is the most promising direction \citep{DBLP:conf/iser/EscandeKMG08}.
However, this direction raises two theoretical questions that remain to be solved, or even to be properly formulated. \\

\noindent \textbf{Regarding $\mathcal{P}_1$}, the guide path must guarantee the existence of a contact sequence to actuate it (This property is related to the controllability of the root actuated by the contact forces). We call this property \textit{true feasibility}. This property has not been studied yet; the only way to validate a waypoint in the path is to explicitly compute the contact locations and forces, which is computationally not reasonable \citep{Bouyarmane2009}, unless the scenario is limited to cyclic, quasi-flat cases \citep{zucker2010optimization}. \\

\noindent \textbf{Regarding $\mathcal{P}_2$}, there are infinite combinations of possible contact sequences for a given root path. The selection of one particular contact sequence with interesting properties (minimum number of contact changes, robustness, efficiency or naturalness) has been studied for cyclic cases \citep{Hauser06usingmotion}, but has not been efficiently applied to cluttered environments (\citeauthor{bouyarmane:lirmm-00777727, DBLP:conf/iser/EscandeKMG08} mostly randomly picked one contact sequence, leading to possibly very tedious transitions).  \\

@@

Compared to previous work \citep{Mordatch:2012:DCB:2185520.2185539} our planner does not produce a complete motion, but a discrete sequence of contacts.
Since the interpolation of a complete path between such configurations can be solved within real-time constraints \citep{Carpentier2016}, we claim that our planner
is the fastest multi-contact planning solution to our knowledge.

\begin{figure*}
  \centering
  \begin{overpic}[width=0.8\linewidth]{figures/workflow}
    %~ \put (6.4,1.8) {\normalsize{Request}} 
    \put (30,10.8) {\large{\color{white}\Pa} }
    %~ \put (31.6,2) {\scriptsize{\color{white}RB-RRT}} 
    \put (66.4,10.8) {\large{\color{white}\Pb} }
    %~ \put (72.5,2) {\tiny{\color{white}Contact}} 
  \end{overpic}
  \vspace{-1em}
  \caption{
    Overview of our 2-stage framework. \Pa: Given a path request between the yellow and blue positions, a guide path is computed in the space of truly feasible guides $C_{reach}$. This is achieved by defining a geometric condition, the reachability condition (abstracted here with the transparent cylinders). \Pb: The path is extended into a discrete sequence of contact configurations using an iterative algorithm.}
  \label{fig:framework}
\end{figure*}

### 2016-01-17 body/overview.tex
trajectory removed

%
\begin{figure*}
  \centering
  \begin{overpic}[width=0.8\linewidth]{figures/contact_gen}
		\put (1,1) {a} 
		\put (22,1) {b} 
		\put (42,1) {c} 
		\put (62,1) {d} 
		\put (83,1) {e} 
	\end{overpic}
  \caption{Generation of a contact configuration for the right leg of HRP-2. a: Selection of reachable obstacles. b: Entries of the limb samples database (with $N = 4$). c: With a proximity query on the octree database, configurations too far from obstacles are eliminated. d: The best candidate according to a user-defined heuristic $h$ is chosen. e: The final contact is achieved using inverse kinematics.}
  \label{fig:contact_gen}
\end{figure*}
\subsection{Computation of a guide path --- \Pa}
We first consider the problem of planning a relevant guide path. The objective is to compute a path of root placements that will allow contact creation. A desired requirement is to preserve the completeness of the planner: it should be able to explore any possible guide trajectory, but at the same time, any computed guide trajectory must be \textit{truly feasible}, i.e. must lead to a valid sequence of contacts.

@@

An intuitive description of root placements satisfying C1 and C2 is ``close, but not too close'': close, because a contact surface must be partially included in the reachable workspace of the robot (represented for the right arm in Figure~\ref{fig:contact_gen}--a); not too close, because the robot must avoid collision. We define formally $C_{reach}$, the set of root placements satisfying C1 and C2, in which we compute a guide trajectory with a sampling-based planner, the Reachability-Based RRT---RB-RRT--- (Figure~\ref{fig:framework}---\Pa). Planning in $C_{reach}$ boils down to planning in SE(3), which has an acceptable practical complexity.
%
Details are presented in Section~\ref{rbprm}.

>>>>

%
\begin{figure*}
  \centering
  \begin{overpic}[width=0.8\linewidth]{figures/contact_gen}
		\put (1,1) {a} 
		\put (22,1) {b} 
		\put (42,1) {c} 
		\put (62,1) {d} 
		\put (83,1) {e} 
	\end{overpic}
  \caption{Generation of a contact configuration for the right leg of HRP-2. a: Selection of reachable obstacles. b: Entries of the limb samples database (with $N = 4$). c: With a proximity query on the octree database, configurations too far from obstacles are eliminated. d: The best candidate according to a user-defined heuristic $h$ is chosen. e: The final contact is achieved using inverse kinematics.}
  \label{fig:contact_gen}
\end{figure*}
\subsection{Computation of a guide path --- \Pa}
We first consider the problem of planning a relevant guide path. The objective is to compute a path of root placements that will allow contact creation. A desired requirement is to preserve the completeness of the planner: it should be able to explore any possible guide path, but at the same time, any computed guide path must be \textit{truly feasible}, i.e. must lead to a valid sequence of contacts.

@@

An intuitive description of root placements satisfying C1 and C2 is ``close, but not too close'': close, because a contact surface must be partially included in the reachable workspace of the robot (represented for the right arm in Figure~\ref{fig:contact_gen}--a); not too close, because the robot must avoid collision. We define formally $C_{reach}$, the set of root placements satisfying C1 and C2, in which we compute a guide path with a sampling-based planner, the Reachability-Based RRT---RB-RRT--- (Figure~\ref{fig:framework}---\Pa). Planning in $C_{reach}$ boils down to planning in SE(3), which has an acceptable practical complexity.
%
Details are presented in Section~\ref{rbprm}.

### 2016-01-17 body/rbprm.tex
trajectory removed

For this stage, and for this stage only, we make the assumption that in cluttered environments, a \textit{geometrically feasible} path can be transformed into a \textit{truly feasible} path.
Under this assumption, for a two-stage acyclic contact planner to be exact and complete, we need the combination of two conditions on a guide trajectory generator: all the generated trajectories must be \textit{geometrically feasible} (sufficient condition); the guide planner must be complete, i.e. it must be able to discover any \textit{geometrically feasible} trajectory (necessary condition).

@@

The condition $C_{reach}^1$ is only necessary which means that one such root placement might not be truly feasible: in practice it is not guaranteed to find a valid sequence of contacts for every guide trajectory in $C_{reach}^1$.

@@

In general, the inclusion is strict, which means that we lose the completeness of the two-stage contact planner (i.e. the planner is not able to discover a trajectory inside \mbox{$C_{reach} \setminus C_{reach}^\infty$}). However, the sufficient condition guarantees that any such trajectories leads to a valid sequence of contacts (i.e. $\pi$ is defined).

\subsection{Geometrical feasibility: a compromise reachability condition}
The sufficient condition is not interesting in practice since it leads the solver to lose too many interesting trajectories. The necessary condition is not perfect either, since the first stage of the planner would stop on a guide that is not \textit{geometrically feasible} in practice. It might be possible to find a shape $B$ that is necessary and sufficient; however, it seems intuitively very unlikely in general. The construction of a shape $W^0 \subset B \subset B^{max}$ leading to a necessary and sufficient condition (or the proof of its nonexistence) is out of the scope of this work.

@@

\subsection{Computing the guide trajectory in $C_{reach}^s$}
Once a value of $s$ has been fixed, any sampling-based motion planner can be used to plan a trajectory in $C_{reach}^s$. 
Indeed, contrary to $C_{Contact}$,  $C_{reach}^s$ has a non zero measure in the configuration space $C$. Therefore a standard uniform sampling approach
can work, in spite of a high rejection rate. 
Thus, the only significant change regarding a classical planner is to replace the classical collision checking method with a test of belonging to $C_{reach}^s$ when verifying
that drawn configurations and associated local paths are valid.

>>>>

For this stage, and for this stage only, we make the assumption that in cluttered environments, a \textit{geometrically feasible} path can be transformed into a \textit{truly feasible} path.
Under this assumption, for a two-stage acyclic contact planner to be exact and complete, we need the combination of two conditions on a guide path generator: all the generated paths must be \textit{geometrically feasible} (sufficient condition); the guide planner must be complete, i.e. it must be able to discover any \textit{geometrically feasible} path (necessary condition).

@@

The condition $C_{reach}^1$ is only necessary which means that one such root placement might not be truly feasible: in practice it is not guaranteed to find a valid sequence of contacts for every guide path in $C_{reach}^1$.

@@

In general, the inclusion is strict, which means that we lose the completeness of the two-stage contact planner (i.e. the planner is not able to discover a path inside \mbox{$C_{reach} \setminus C_{reach}^\infty$}). However, the sufficient condition guarantees that any such path leads to a valid sequence of contacts (i.e. $\pi$ is defined).

\subsection{Geometrical feasibility: a compromise reachability condition}
The sufficient condition is not interesting in practice since it leads the solver to lose too many interesting paths. The necessary condition is not perfect either, since the first stage of the planner would stop on a guide that is not \textit{geometrically feasible} in practice. It might be possible to find a shape $B$ that is necessary and sufficient; however, it seems intuitively very unlikely in general. The construction of a shape $W^0 \subset B \subset B^{max}$ leading to a necessary and sufficient condition (or the proof of its nonexistence) is out of the scope of this work.

@@

\subsection{Computing the guide path in $C_{reach}^s$}
Once a value of $s$ has been fixed, any sampling-based motion planner can be used to plan a path in $C_{reach}^s$. 
Indeed, contrary to $C_{Contact}$,  $C_{reach}^s$ has a non zero measure in the configuration space $C$. Therefore a standard uniform sampling approach
can work, in spite of a high rejection rate. 
Thus, the only significant change regarding a classical planner is to replace the classical collision checking method with a test of belonging to $C_{reach}^s$ when verifying
that drawn configurations and associated local paths are valid.
